\papertitle

### 2024-01-11 src/tex/ms.tex
To run on HPC

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
    \includegraphics[width=\columnwidth]{glswlsols.pdf}
    \script{glswlsols.py}
    \caption{
        Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
        from MSD data from \num{4096} individual simulations of \num{128} particles undergoing a \SI{128}{step} 3D lattice random walk, with a step size chosen so that the true diffusion coefficient $\D = 1$.
        In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
    \label{fig:glswlsols}
\end{figure}

@@

To illustrate the complete numerical procedure for deriving the model covariance matrix, $\bm{\Sigma^\prime}$, we present in Fig.~\ref{fig:covariances} the MSD covariance matrix for \num{4096} random-walk simulations, as described above, at three differing levels of approximation:
the numerically converged covariance matrix, $\bm{\Sigma}$, computed using the data from all \num{4096} simulations (Fig.~\ref{fig:covariances}a);
the corresponding analytical model covariance matrix, $\mathbf{\Sigma^\prime}$, defined by Eqn.~\ref{equ:cvv} and parametrised using analytical variances $\var{\oMSDi}$ (Fig.~\ref{fig:covariances}b); and the average model covariance matrix obtained by parametrising Eqn.~\ref{equ:cvv} using smoothed variances estimated from individual simulation trajectories, and averaging over the resulting set of all \num{4096} matrices (Fig.~\ref{fig:covariances}c).
%
\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure3.pdf}}
    \includegraphics[width=\columnwidth]{covariances.pdf}
    \script{covariances.py}
    \caption{
        (a) The numerical MSD covariance matrix $\bm{\Sigma}$ calculated using MSD data from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle.
        (b) The analytical MSD covariance matrix $\bm{\Sigma^\prime}$ (Eqn.~\ref{equ:cvv}), parametrised using analytical random-walk variances $\var{\oMSDi}$.
        (c) The MSD covariance matrix obtained applying the numerical scheme described in the main text to each individual random walk simulation, averaged over all \num{4096} such simulations.
        Colour bars in (a--c) show the covariance, $\Sigma\left[\oMSDi, \oMSDj\right]$.
        The off-diagonal panels show difference plots, computed as per-element ratios between pairs of covariance matrices (a--c).
        %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
    }
    \label{fig:covariances}
\end{figure}
%

@@

\begin{figure*}[ht!]
    \centering
    % \resizebox{\textwidth}{!}{\includegraphics*{figure4.pdf}}
    \includegraphics[width=\textwidth]{random_walk.pdf}
    \script{random_walk.py}
    \caption{
        (a) Observed MSD from a single simulation of 128 particles undergoing a 3D-lattice random walk of 128 steps per particle (dark line).
        The green shading shows the corresponding posterior distribution $\prob{\model|\oMSD}$ of linear models compatible with the observed MSD data $\oMSD$, calculated using the scheme described in the main text.
        The variegated shading indicates compatibility intervals of \SIlist[list-final-separator = {, and }]{1;2;3}{\sigma}$[\prob{\model|\oMSD}]$.
        (b) The marginal posterior distribution $\prob{\Dest|\oMSD}$ obtained from the posterior distribution of linear models in (a).
        The mean of this distribution gives the point estimate $\Dest$ for this simulation input data.
        The blue horizontal bar shows an interval of one standard deviation in $\prob{\Dest|\oMSD}$.
        (c) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations.
        Each simulation has been analysed as in (a) and (b) to yield a single corresponding point estimate $\Dest$.
        The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
        The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
        (d) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
    } 
    \label{fig:random_walk}
\end{figure*}

@@

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
    \includegraphics[width=\columnwidth]{pyblock.pdf}
    \script{pyblock.py}
    \caption{Comparison of the distribution of $\Dest$ (a, c, \& e) and the estimated variances (b, d, \& f) from 4096 individual random walk simulations using variances approximated by Eqn.~\ref{equ:varestMSD} (a \& b), from block averaging with fitting to Eqn.~\ref{equ:variance} (c \& d), and without fitting (e \& f). Note that the bounds in a, c, \& e are defined by the extrema of the estimated values, showing the fact that without the fitting to Eqn.~\ref{equ:variance}, the resulting covariance matrix is numerically unstable.}
    \label{fig:pyblock}
\end{figure}

>>>>

% \begin{figure}
%     \centering
%     % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
%     \includegraphics[width=\columnwidth]{glswlsols.pdf}
%     \script{glswlsols.py}
%     \caption{
%         Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
%         from MSD data from \num{4096} individual simulations of \num{128} particles undergoing a \SI{128}{step} 3D lattice random walk, with a step size chosen so that the true diffusion coefficient $\D = 1$.
%         In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
%     \label{fig:glswlsols}
% \end{figure}

@@

To illustrate the complete numerical procedure for deriving the model covariance matrix, $\bm{\Sigma^\prime}$, we present in Fig.~\ref{fig:covariances} the MSD covariance matrix for \num{4096} random-walk simulations, as described above, at three differing levels of approximation:
the numerically converged covariance matrix, $\bm{\Sigma}$, computed using the data from all \num{4096} simulations (Fig.~\ref{fig:covariances}a);
the corresponding analytical model covariance matrix, $\mathbf{\Sigma^\prime}$, defined by Eqn.~\ref{equ:cvv} and parametrised using analytical variances $\var{\oMSDi}$ (Fig.~\ref{fig:covariances}b); and the average model covariance matrix obtained by parametrising Eqn.~\ref{equ:cvv} using smoothed variances estimated from individual simulation trajectories, and averaging over the resulting set of all \num{4096} matrices (Fig.~\ref{fig:covariances}c).
%
% \begin{figure}
%     \centering
%     % \resizebox{\columnwidth}{!}{\includegraphics*{figure3.pdf}}
%     \includegraphics[width=\columnwidth]{covariances.pdf}
%     \script{covariances.py}
%     \caption{
%         (a) The numerical MSD covariance matrix $\bm{\Sigma}$ calculated using MSD data from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle.
%         (b) The analytical MSD covariance matrix $\bm{\Sigma^\prime}$ (Eqn.~\ref{equ:cvv}), parametrised using analytical random-walk variances $\var{\oMSDi}$.
%         (c) The MSD covariance matrix obtained applying the numerical scheme described in the main text to each individual random walk simulation, averaged over all \num{4096} such simulations.
%         Colour bars in (a--c) show the covariance, $\Sigma\left[\oMSDi, \oMSDj\right]$.
%         The off-diagonal panels show difference plots, computed as per-element ratios between pairs of covariance matrices (a--c).
%         %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
%     }
%     \label{fig:covariances}
% \end{figure}
%

@@

% \begin{figure*}[ht!]
%     \centering
%     % \resizebox{\textwidth}{!}{\includegraphics*{figure4.pdf}}
%     \includegraphics[width=\textwidth]{random_walk.pdf}
%     \script{random_walk.py}
%     \caption{
%         (a) Observed MSD from a single simulation of 128 particles undergoing a 3D-lattice random walk of 128 steps per particle (dark line).
%         The green shading shows the corresponding posterior distribution $\prob{\model|\oMSD}$ of linear models compatible with the observed MSD data $\oMSD$, calculated using the scheme described in the main text.
%         The variegated shading indicates compatibility intervals of \SIlist[list-final-separator = {, and }]{1;2;3}{\sigma}$[\prob{\model|\oMSD}]$.
%         (b) The marginal posterior distribution $\prob{\Dest|\oMSD}$ obtained from the posterior distribution of linear models in (a).
%         The mean of this distribution gives the point estimate $\Dest$ for this simulation input data.
%         The blue horizontal bar shows an interval of one standard deviation in $\prob{\Dest|\oMSD}$.
%         (c) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations.
%         Each simulation has been analysed as in (a) and (b) to yield a single corresponding point estimate $\Dest$.
%         The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
%         The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
%         (d) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
%     } 
%     \label{fig:random_walk}
% \end{figure*}

@@

% \begin{figure}
%     \centering
%     % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
%     \includegraphics[width=\columnwidth]{pyblock.pdf}
%     \script{pyblock.py}
%     \caption{Comparison of the distribution of $\Dest$ (a, c, \& e) and the estimated variances (b, d, \& f) from 4096 individual random walk simulations using variances approximated by Eqn.~\ref{equ:varestMSD} (a \& b), from block averaging with fitting to Eqn.~\ref{equ:variance} (c \& d), and without fitting (e \& f). Note that the bounds in a, c, \& e are defined by the extrema of the estimated values, showing the fact that without the fitting to Eqn.~\ref{equ:variance}, the resulting covariance matrix is numerically unstable.}
%     \label{fig:pyblock}
% \end{figure}
